### 2021-10-24 README.Rmd
Updated readme pacakge description

`ggmatplot` plots two matrices against each other using [`ggplot2`](https://ggplot2.tidyverse.org/)

@@

You can install the released version of ggmatplot from [GitHub](https://github.com/xuan-liang/ggmatplot):

@@

>>>>

`ggmatplot` is a quick and easy way of plotting the columns of two matrices against each other. It is built upon [ggplot2](https://ggplot2.tidyverse.org/), and is aimed at providing a more direct and simple approach to creating plots using matrices.

`ggmatplot` can also be considered as an alternative to pivoting data into long format for visualizing using `ggplot2`.

@@

You can install the released version of `ggmatplot` from [GitHub](https://github.com/xuan-liang/ggmatplot):

@@

## Examples

```{r message=FALSE}
library(ggmatplot)
```

```{r}
USPersonalExpenditure

ggmatplot(
  rownames(USPersonalExpenditure),
  USPersonalExpenditure[, 1:5],
  plot_type = "point",
  xlab = "Category",
  ylab = "Expenditure (in Billions of Dollars)",
  legend_title = "Year",
  legend_label = c(1940, 1945, 1950, 1955, 1960)
) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
